---
title: "Exercise 2 Part 2"
author: "Team 2"
date: "2023-01-24"
output:
  github_document: default
  pdf_document: default
---
# Import the Data
```{r}
aus = read.csv('C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/examiner_aus.csv')
gs = read.csv('C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/examiner_gs.csv')
ids = read.csv('C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/examiner_ids.csv')
```

```{r, message = FALSE, warning = FALSE}
library(arrow)
app = read_parquet('C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/app_data_sample.parquet')
```

# Panel Dataset of Quaterly Aggregated Production Measure for Each Examiner
## Number of new applications
```{r, warning = FALSE}
library(lubridate)
library(dplyr)
app$quarter = quarter(app$filing_date, type = 'year.quarter')
new_app = app %>% group_by(examiner_id, quarter) %>% summarize(new_app = n())
new_app
```

## Number of abandoned applications
```{r, warning = FALSE}
library(lubridate)
library(dplyr)
app$quarter_aban = quarter(app$abandon_date, type = 'year.quarter')
aban_app = app %>% group_by(examiner_id, quarter_aban) %>% summarize(aban_app = n())
aban_app
```

Number of allowed applications
```{r, warning = FALSE}
library(lubridate)
library(dplyr)
app$quarter_allow = quarter(app$patent_issue_date, type = 'year.quarter')
allow_app = app %>% group_by(examiner_id, quarter_allow) %>% summarize(allow_app = n())
allow_app
```

Number of applications still in-process
```{r, warning = FALSE}
library(lubridate)
library(dplyr)

app$abandon_date = as.character(app$abandon_date)
app$patent_issue_date = as.character(app$patent_issue_date)
prog_app = app %>% group_by(examiner_id, quarter) %>% summarize(prog_app = sum((is.na(abandon_date) && is.na(patent_issue_date))))
prog_app
```

# Art Units
Current Art Unit
```{r}
library(dplyr)
current_art = app %>% group_by(quarter) %>% summarize(current_art = n_distinct(examiner_art_unit))
current_art
```

Number of people in art unit
```{r, warning = FALSE}
library(dplyr)
people_art = app %>% group_by(quarter, examiner_art_unit) %>% summarize(current_art = n())
people_art
```

Number of women in art unit
```{r, include = FALSE}
# DO NOT RUN THIS CELL
# library(lubridate)
# library(dplyr)
# app$quarter = quarter(app$filing_date, type = 'year.quarter')
# gender$examiner_id = gender$patex_id
# gender1 = gender[, c('examiner_id', 'gender2')]

# app2 = app[, c('quarter', 'examiner_id', 'examiner_art_unit')]
# app2 = merge(x = app2, y = gender1, by = 'examiner_id', all.x = TRUE)
# write.csv(app2, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/app2.csv', row.names = FALSE)
```

```{r}
app2 = read.csv('C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/app2.csv')
```

```{r, warning = FALSE}
library(dplyr)
art_gender = app2 %>% group_by(quarter, examiner_art_unit, gender2) %>% summarize(current_art = n())
art_gender
```

Number of examiners by race in art unit
```{r, message = FALSE, warning = FALSE}
# DO NOT RUN THIS CELL
# library(lubridate)
# library(dplyr)
# app$quarter = quarter(app$filing_date, type = 'year.quarter')

# race1 = merge(x = indiv_race, y = ids, by = 'old_pid', all.x = TRUE)
# race1 = race1[, c('patex_id', 'race')]
# race1$examiner_id = race1$patex_id

# app1 = app[, c('quarter', 'examiner_id', 'examiner_art_unit')]
# app1 = merge(x = app1, y = race1, by = 'examiner_id', all.x = TRUE)
# write.csv(app1, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/app1.csv', row.names = FALSE)
```

```{r}
app1 = read.csv('C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/app1.csv')
```

```{r, warning = FALSE}
library(dplyr)
art_race = app1 %>% group_by(quarter, examiner_art_unit, race) %>% summarize(current_art = n())
art_race
```



# Indicators
Separation indicator (examiner left the USPTO)
```{r}
indiv = read.csv('C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/indiv.csv')
separation_ind = as.data.frame(indiv$new_pid)
id_in_gs = unique(gs$new_pid)
separation_ind$sep_ind = !(indiv$new_pid %in% id_in_gs)
separation_ind
```

AU move indicator (examiner changed art units)
```{r}
move_ind = gs %>% group_by(new_pid) %>% summarize(current_art = n())
move_ind = transform(move_ind, move_ind = ifelse(current_art == 1, FALSE, TRUE))
move_ind
```


# Export all dataframes
```{r}
write.csv(new_app, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/new_app.csv', row.names = FALSE)
write.csv(aban_app, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/aban_app.csv', row.names = FALSE)
write.csv(allow_app, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/allow_app.csv', row.names = FALSE)
write.csv(prog_app, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/prog_app.csv', row.names = FALSE)
write.csv(current_art, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/current_art.csv', row.names = FALSE)
write.csv(people_art, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/people_art.csv', row.names = FALSE)
write.csv(art_gender, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/art_gender.csv', row.names = FALSE)
write.csv(art_race, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/art_race.csv', row.names = FALSE)
write.csv(separation_ind, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/separation_ind.csv', row.names = FALSE)
write.csv(move_ind, 'C:/Users/jinho/Documents/2023-ta-assignments/exercise2_data/move_ind.csv', row.names = FALSE)
```
